What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd
Tightening up third paragraph
Rewriting a few parts of this paragraph to help the flow a bit.

<!--MP ➔ The paragraph below is an attempt to segue to the aim of our study before getting into the lit review – I'm always of fan of making the general aim of the study clear by the end of the first paragraph. I've summarised the sentiment of the original first two paragraphs a bit (and struck out tangential sentences). I'd suggest this could make the first paragraph of the paper – highlighting the the research context and the gap that is driving our study-->

@@

Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that the next generation of researchers can produce research which is more replicable than that of the last. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology. However, the question of how best to provide this understanding is by no means trivial to answer. Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.

@@

# gender --> need to run through gendercoder [breadcrumb!]

>>>>

@@

Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that thay may produce research that is even more replicable than that of previous generations. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. However, how we best provide this understanding is no trivial task. Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.

@@

# gender --> need to summarise once we've recoded it in preprocessing script
  # [breadcrumb]
